AXIELL R HACKS

### 2024-03-25 _GEN_axi_Rhacks.Rmd
long time no commit, JMCB 2nd round IP
JMCB 2 - progress

@@

ch <- sample_n(df, 10) # n=10
```

@@

# Return names which have more than one row of data
data %>% 
  group_by(name) %>% 
  filter(n() != 1)
```

@@

### extract all letters

>>>>

### CLIPBOARD

```{r}
write.table(df, "clipboard", sep="\t", row.names=FALSE)
```

@@

ch <- sample_n(df, 10) # n=10

# random sample with selected columns

sample_n(aa, 10) %>% select(rok, prirc, porc104, subc105, prirc4)
```

@@

# Return names which have more than one row of data
data %>% 
  group_by(name) %>% 
  filter(n() != 1)

# priznak
data %>% 
  group_by(name) %>% 
  mutate(priznak = ifelse(n()!=1), 1, 0)
```

@@

### extract all (except) letters

```{r}
str_detect(invc, "[A-Za-z]")
str_extract_all(invc, "[^a-zA-Z]")

### extract part ending with space or EOF

(?:\\s|$): This part matches either a whitespace character (\\s) or the end of the string ($). The (?: ... ) is a non-capturing group, which allows us to group the alternatives without capturing them as a separate match.

```{r}
extracted <- str_extract(text, "c\\.j\\..*?(?:\\s|$)")
```
